% !TXS template
\documentclass[11pt]{memoir}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper]{geometry}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{float}
\usepackage{hyperref}
\usepackage{multicol}
\setcounter{tocdepth}{3}
\setcounter{secnumdepth}{3}
\usepackage[font={small,it}]{caption}
%%\usepackage[margin=1.4in]{geometry}
%%\usepackage{babel}

%\addto\captionsfrench{% Replace "english" with the language you use
%	\renewcommand{\contentsname}%
%	{}%
%}
\renewcommand{\printtoctitle}[1]{\Huge \textbf{Table of Content}}

\renewcommand\thefigure{\arabic{figure}}
\renewcommand\thetable{\arabic{table}}
\setcounter{figure}{0}
\renewcommand{\thesection}{\arabic{section}}
\begin{document}

\title{Apprenticeship thesis, 2nd years \\ \textbf{Master of Computer Science}, speciality \textbf{Ingénierie du
		Logiciel et des Connaissances} 
	
	\bigskip
	{\huge Realtime continous optimisation of healthcare transportation fleets using massively parallele memetic algorithm on GPGPU} \\	
	}
\author{Joseph Pallamidessi\\ University of Strasbourg} 
\date{\vspace{4.0in}
	
\protect\raggedright
{\normalsize Maître d'alternance:} \\
		\textbf{Pierre Collet}, Université de Strasbourg \\
		\textbf{Guillaume Philips}, Synovo SAS}

\maketitle
\newpage

\tableofcontents*
\newpage


\section{Acknowlegments}\label{Acknowledgements}

I would first like to thank professor Collet, for the guidance provided during those
two year of apprenticeship. It is because of him that today I stand before you,
having opened to me the wonderful world of universitary research. \\
Guillaume Philip, my apprenticeship tutor inside Synovo to having me let experiment, test
and gave full liberty to conduit my research on this problem during the one and a
half year that I spent inside his company. He was always listening, throughful and
focus even when the obstacle seemed inreachable. He was flexibility, availability
and focus are something that I wish to encounter again in my carrier, as it gave me
the strength to finish this big challenge. \\
I would like to thanks Synovo and the ICube laboratories for their support and
letting me work in this big collaboration between university researchers and the
corporate world.

\section{Abstract}
We developed a distributed multi-objectives genetic algorithm for solving a special case of
large vehicle routing for healthcare service. The goal of this algorithm is to
replace the task of planification for the next day currently done by human operator and with
minor modification,due to the evolutionary nature of the used techniques, be able to
done realtime continuous optimization. The problem in itself is highly constrained
but the search space remais large enough to require heuristics. The help the
exploitation phase, a set of local searches, the most used in combinatory
optimization have been reimplemented to take into account the specificities and
multi-objective nature of the problem. \\
The optimization must be fast enough with large instance to compete with humans as
this field is  caracterised by high frequence of modification through the day . In
order to avoid the traditional computational pitfall of pareto-based selection, a
novel selection method (G-ASREA) on GPGPU has been succesfully implemented and tested with
speed-up ranging for 4 to 50 times faster than the NSGAII algorithm while providing
better population diversity and overall results.

\section{Introduction}
Planification of large instance remains an open field of research. The particular
problem of vehicle routing of healthcare service is twofolds : due to its
various constraints it is difficult to extract to ontology needed for modelizing for
a linear solver and the sheer number of element to optimize make it out of reach for
the classical exact algorithm, thus the need of powerful heuristics and
metaheuristic.
\subsection{Problem definition}

\subsection{Healthcare transportation specificities}
\label{sub:Healthcare transportation specificities}

\section{Context of research}
\label{sec:Context of research}


\section{État de l'art}
\section{Local searches}
\subsection{Time-window constrained 2-opt*}
\subsubsection{Base algorithm}
\subsubsection{TW-flavored version}
\subsection{or-exchange}
\subsection{RAR}
\subsection{Spliting and merging}
\subsection{Fuzzing}

\section{Result}
\subsection{Metrics definitions}

\subsection{G-ASREA vs NSGAII}
\subsubsection{Execution time}
\subsubsection{Quality of results}

\paragraph{Per generations}

\paragraph{Observation}

\subsection{Comparaison against human operators}

\section{Discussion}

\section{Conclusion}

\nocite{*}
\bibliographystyle{plain}
\bibliography{mémoire}

\end{document}
